---
title: "Habits"
author: Tie Ma
date: March 22, 2005
output: powerpoint_presentation

---

```{r include=FALSE}
library("ggplot2")
library("fpp2")
library("tidyr")
library("forecast")
library("readr")
library("ggfortify")
library("tseries")
library("urca")
library("readxl")
library("lubridate")
library("cansim")       
library("tsbox")
library("RColorBrewer")
library("wesanderson")

Can_housing_sell_data.raw <- read_excel("/Users/tie/Documents/GitHub/ECON-493-forcasting-economy/The research project/News_release_chart_data_mar_2023.xlsx", sheet = "Chart A", col_types = c("date",  "numeric", "numeric", "skip", "skip"))
#yes,they do got other data, which is boring to be honest. 

Can_month_housing_sell.ts <- ts(Can_housing_sell_data.raw$Canada, start = c(2007, 1), end = c(2023, 2), frequency = 12)
```

## The Canadian housing market sales date

-   This time series collected by the Canadian Real Estate association (CREA) on the Canadian housing sales from Jan 2007 to Jan 2023.

-   why this data?

    -   because this is the only interest data with at least 100 observation related to the housing market.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
autoplot(Can_month_housing_sell.ts, 
         xlab = "time", ylab = "housing sell", main = "Canadian housing sell", 
         geom = c("line"), label = T, truncate.gaps = FALSE,
         Label.color = "#90aac0",  colour = "#003b6f" ) + 
  theme(plot.background = element_rect(fill = "#C0CEDB"),
        panel.background = element_rect(fill = "#E0E7ED"),
        plot.caption = element_text(hjust = 0, vjust = 0, margin = margin(t = 5, unit = "pt")))
```

## Some found on the data.

-   The data is randomly walking or close to randomly walking.

-   The auto.arima function I used while I Played with my data.

-   This auto.arima setting force auto,arima() to search 15625 combinations of ARIMA from ARIMA(1,1,1)(1,1,1) go to ARIMA (5,5,5)(5,5,5) it will consume a huge amount of computing power. It take my computre around 30s.

```{r eval = FALSE}
all_data_model_1 <- auto.arima(Can_month_housing_sell.ts, 
                                approximation = FALSE, 
                                parallel = TRUE, 
                                stepwise = FALSE, 
                                max.Q = 5, max.P = 5, max.D = 5,
                                max.d = 5, max.p = 5, max.q = 5)
```

-   will it work better compare to auto.arima() in default setting?
-   no.

## The data analysis for entire time series.

```{r eval = FALSE}
all_data_model_1 <- auto.arima(Can_month_housing_sell.ts, 
                                approximation = FALSE, 
                                parallel = TRUE, 
                                stepwise = FALSE,
                                max.Q = 5, max.P = 5, max.D = 5,
                                max.d = 5, max.p = 5, max.q = 5)
print(all_data_model_1)     
#ARIMA(2,1,0) 

### so, what dos the default auto-arima will give me and how long it take?
#0.025s and ARIMA(0,1,1)

all_data_model_2 <- auto.arima(Can_month_housing_sell.ts)
print(all_data_model_2)
#ARIMA(0,1,1) random walk with draft.

#######################so, which one is better? 

######compare the AIC?
AIC(all_data_model_2)
AIC(all_data_model_1)

```

## How about not including the 2008 finical crash? 
```{R echo=FALSE}
#constructed model 2: what if we do not including the data from before the 2008 the economic crisis?
after_2008_forecasting_data <- window(Can_month_housing_sell.ts, start= c(2009,7), end= c(2023,2))
#plot the graphy
autoplot(after_2008_forecasting_data)
```

Result
ARIMA(0,1,1)
AIC: 3041.171
ARIMA(2,1,0)
AIC: 3038.807
still, random walk with drift? 


## How about 3 years before and after 2020 when the covid start to impact canada? 

```{R}
The_before_during_after_Covid_model.data<-window(Can_month_housing_sell.ts, start= c(2017,1), end= c(2023,2))
autoplot(The_before_during_after_Covid_model.data)
```

still ARIMA(2,1,0) and ARIMA(0,1,1) the random walk drift.
even the AIC is supre close 
AIC(The_before_during_after_Covid_model_1)
#1413.121
AIC(The_before_during_after_Covid_model_2)
#1413.473


## constructed model 2: what if we only including the data from 2020 alone? 

```{r, cars, fig.cap="A scatterplot.", echo=FALSE}
The_2022_along.data<-window(Can_month_housing_sell.ts, start= c(2020,1), end= c(2023,2))
autoplot(The_2022_along.data)
```

Both auto.arima suggest the data is random walk with ARIMA(0,1,1)



## So, here is my forecasting base on all the model I got from auto.arima

```{R include=FALSE}
all_data_model_1 <- auto.arima(Can_month_housing_sell.ts, 
                                approximation = FALSE, 
                                parallel = TRUE, 
                                stepwise = FALSE,
                                max.Q = 5, max.P = 5, max.D = 5,
                                max.d = 5, max.p = 5, max.q = 5)
all_data_model_2 <- auto.arima(Can_month_housing_sell.ts)
after_2008_forecasting_model_1 <- auto.arima(after_2008_forecasting_data, 
                               approximation = FALSE, 
                               parallel = TRUE, 
                               stepwise = FALSE,
                               max.Q = 5, max.P = 5, max.D = 5,
                               max.d = 5, max.p = 5, max.q = 5)
after_2008_forecasting_model_2 <- auto.arima(after_2008_forecasting_data)
The_before_during_after_Covid_model_1 <- auto.arima(The_before_during_after_Covid_model.data, 
                                             approximation = FALSE, 
                                             parallel = F, 
                                             stepwise = FALSE,
                                             max.Q = 5, max.P = 5, max.D = 5,
                                             max.d = 5, max.p = 5, max.q = 5)
The_before_during_after_Covid_model_2 <- auto.arima(The_before_during_after_Covid_model.data, d=1)
The_2020_along.data<-window(Can_month_housing_sell.ts, start= c(2020,1), end= c(2023,2))
The_2020_along_model_1<- auto.arima(The_2020_along.data, 
                                                    approximation = FALSE, 
                                                    parallel = T, 
                                                    stepwise = FALSE,
                                                    max.Q = 5, max.P = 5, max.D = 5,
                                                    max.d = 5, max.p = 5, max.q = 5)
The_2020_along_data_model_2 <- auto.arima(The_2020_along.data)

##### The forecast part 
all_data_model_1_forecast <- forecast(all_data_model_1, h = 6)
all_data_model_2_forecast <- forecast(all_data_model_2, h = 6)
after_2008_forecasting_model_1_forecast <- forecast(after_2008_forecasting_model_1, h = 6)
after_2008_forecasting_model_2_forecast <- forecast(after_2008_forecasting_model_2, h = 6)
The_before_during_after_Covid_model_1_forecast <- forecast(The_before_during_after_Covid_model_1, h = 6)
The_before_during_after_Covid_model_2_forecast <- forecast(The_before_during_after_Covid_model_2, h = 6)
The_2020_along_model_1_forecast <- forecast(The_2020_along_model_1, h = 6)
The_2020_along_data_model_2_forecast <- forecast(The_2020_along_data_model_2, h = 6)

```

```{R echo=FALSE}
# Plot the first forecast
plot(all_data_model_1_forecast, main = "Forecasts for all model", xlab = "Time", ylab = "Housing Sell", col = "black")

# Add the other forecasts to the plot using lines()
lines(all_data_model_2_forecast$mean, col = "#FE2712")
lines(after_2008_forecasting_model_1_forecast$mean, col = "#FC600A")
lines(after_2008_forecasting_model_2_forecast$mean, col = "#FB9902")
lines(The_before_during_after_Covid_model_1_forecast$mean, col = "#FCCC1A")
lines(The_before_during_after_Covid_model_2_forecast$mean, col = "#B2D723")
lines(The_2020_along_model_1_forecast$mean, col = "#347C98")
lines(The_2020_along_data_model_2_forecast$mean, col = "#4424D6")

```

```{r echo=FALSE}
plot(all_data_model_2_forecast$mean, col = "#FE2712", main = "compare all the forecasting outcome", xlab = "time", ylim = c(34000, 34600), lwd = 2)
lines(all_data_model_1_forecast$mean, col = "#FFA07A", lwd = 2)
lines(after_2008_forecasting_model_1_forecast$mean, col = "#8b4513", lwd = 2)
lines(after_2008_forecasting_model_2_forecast$mean, col = "#FB9902", lwd = 2)
lines(The_before_during_after_Covid_model_1_forecast$mean, col = "#FCCC1A", lwd = 2)
lines(The_before_during_after_Covid_model_2_forecast$mean, col = "#B2D723", lwd = 2)
lines(The_2020_along_model_1_forecast$mean, col = "#347C98", lwd = 2)
lines(The_2020_along_data_model_2_forecast$mean, col = "#4424D6", lwd = 2)

legend("bottomleft", legend = c("All Data Model 2", "All Data Model 1", "After 2008 Model 1", "After 2008 Model 2", "Before/During/After COVID Model 1", "Before/During/After COVID Model 2", "2020 Model 1", "2020 Model 2"), col = c("#FE2712", "#FFA07A", "#8b4513", "#FB9902", "#FCCC1A", "#B2D723", "#347C98", "#4424D6"), lty = 1, lwd = 2)

```


```{r echo=FALSE}
plot(all_data_model_2_forecast$mean, col = "#FE2712", main = "compare all the forecasting outcome", xlab = "time", lwd = 2)
lines(all_data_model_1_forecast$mean, col = "#FFA07A", lwd = 2)
lines(after_2008_forecasting_model_1_forecast$mean, col = "#8b4513", lwd = 2)
lines(after_2008_forecasting_model_2_forecast$mean, col = "#FB9902", lwd = 2)
lines(The_before_during_after_Covid_model_1_forecast$mean, col = "#FCCC1A", lwd = 2)
lines(The_before_during_after_Covid_model_2_forecast$mean, col = "#B2D723", lwd = 2)
lines(The_2020_along_model_1_forecast$mean, col = "#347C98", lwd = 2)
lines(The_2020_along_data_model_2_forecast$mean, col = "#4424D6", lwd = 2)

legend("bottomleft", legend = c("All Data Model 2", "All Data Model 1", "After 2008 Model 1", "After 2008 Model 2", "Before/During/After COVID Model 1", "Before/During/After COVID Model 2", "2020 Model 1", "2020 Model 2"), col = c("#FE2712", "#FFA07A", "#8b4513", "#FB9902", "#FCCC1A", "#B2D723", "#347C98", "#4424D6"), lty = 1, lwd = 2)

```


```{R include=FALSE}
#2.2 The data base import 
everyhingCA_stationary_raw <- read_csv("/Users/tie/Documents/GitHub/ECON-493-forcasting-economy/The research project/LCDMA_February_2023/CAN_MD_asd.xlsx")
#View(everyhingCA.raw)

everyhingCA_raw<- read_csv("/Users/tie/Documents/GitHub/ECON-493-forcasting-economy/The research project/LCDMA_February_2023/CAN_MD.csv") 
#View(everyhingCA_raw)

```

```{r}
######## that is too much data there....

##########The relationship between the housing sell with bank rate?
CA_bank_rate_raw <- "v122550"
CA_bank_rate.st <- get_cansim_vector(CA_bank_rate_raw, start_time = "2007-01-01", end_time = "2023-02-01")
CA_bank_rate_year.st <- year(CA_bank_rate.st$REF_DATE[1])
CA_bank_rate_month.st <- month(CA_bank_rate.st$REF_DATE[1])

#transfer data to the time series time
c(CA_bank_rate_year.st, CA_bank_rate_month.st)
CA_bank_rate.ts <-ts(CA_bank_rate.st$VALUE, start = c(CA_bank_rate_year.st, CA_bank_rate_month.st), freq = 12)
#CA_bank_rate_diff.ts <- diff(CA_bank_rate.ts, lag = 1)

#doing something interesting
housing_sell_plus_policy_rate_model<- auto.arima(Can_month_housing_sell.ts, d =1, 
                                                 xreg = CA_bank_rate.ts, 
                                                 approximation = FALSE, parallel = T, 
                                                 stepwise = FALSE, max.Q = 5, max.P = 5, max.D = 5,
                                                 max.d = 5, max.p = 5, max.q = 5)
print(housing_sell_plus_policy_rate_model)
#Regression with Regression with ARIMA(2,1,2) errors 

x <- 6
# initialize an empty vector to store the values
values <- numeric(length = x)
for (i in 1:x) {
  values[i] <- 4
}
new_bank_data_1 <- print(values)

#print(housing_sell_plus_policy_rate_model)
#checkresiduals(housing_sell_plus_policy_rate_model)
evil_forcast <- forecast(housing_sell_plus_policy_rate_model, h = 6, xreg = new_bank_data)
autoplot(evil_forcast)

#it match with the relationship between the housing market and policy rate.
##################

x <- 6
# initialize an empty vector to store the values
values <- numeric(length = x)
for (i in 1:x) {
  values[i] <- 1
}
new_bank_data_1 <- print(values)

print(housing_sell_plus_policy_rate_model)
#checkresiduals(housing_sell_plus_policy_rate_model)
evil_forcast <- forecast(housing_sell_plus_policy_rate_model, h = 6, xreg = new_bank_data)
autoplot(evil_forcast)


```


```{r}

################# The relationship between housing sell and GPD?
CA_GDP_raw <- "v65201483"
CA_GDP.st <- get_cansim_vector(CA_GDP_raw, start_time = "2005-12-01", end_time = "2022-12-01")
CA_GDP_year.st <- year(CA_GDP.st$REF_DATE[1])
CA_GDP_month.st <- month(CA_GDP.st$REF_DATE[1])
#transfer data to the time series time
c(CA_GDP_year.st, CA_GDP_month.st)
CA_GDP.ts <-ts(CA_GDP.st$VALUE, start = c(CA_GDP_year.st, CA_GDP_month.st), freq = 12)
plot(CA_GDP.ts)

###
CA_GDP_diff.ts <- diff(log(CA_GDP.ts))
plot(CA_GDP_log_diff.ts)
#adf.test(CA_GDP_log_diff.ts)
#The ADF test look good.
###

#create a new time series object using a subset of the data
Can_month_housing_sell_GDP_model.ts <- ts(Can_housing_sell_data.raw$Canada, start = c(2006,1), end = c(2022,12), frequency =12)
plot(Can_month_housing_sell_GDP_model.ts)

housing_sell_plus_GDP_model<- auto.arima(Can_month_housing_sell_GDP_model.ts, xreg= CA_GDP_diff.ts,
                                         approximation = FALSE, parallel = T, stepwise = FALSE, 
                                         max.d = 5, max.p = 5, max.q = 5)
print(housing_sell_plus_GDP_model)

#display the resulting time series
Can_month_housing_sell_GDP_model.ts
adf.test(Can_month_housing_sell_GDP_model.ts)
###


x <- 20
# initialize an empty vector to store the values
values <- numeric(length = x)
for (i in 1:x) {
  values[i] <- 0.01
}
GDP_new_data <- print(values)

housing_sell_plus_GDP_model_forecast <- forecast(PI = T, housing_sell_plus_GDP_model, h = 36, xreg = GDP_new_data)
autoplot(housing_sell_plus_GDP_model_forecast)
######### when the inflation high, the housing sell drop.


#############
#How about the housing sell with the average hourly wage rate?


fix_1<- nnetar(Can_month_housing_sell_GDP_model.ts, xreg = CA_GDP_diff.ts)
fix_forecast <- forecast(fix_1,h=20, xreg =  GDP_new_data)
autoplot(fix_1, PI=f, h = 30)

#THE 
fix_2

##############
#How about the housing sell with the average hourily age? 
hourly_average_wage_raw <- "v2132579"
hourly_average_wag.st <- get_cansim_vector(hourly_average_wage_raw, start_time = "2006-12-01", end_time = "2022-12-01")
hourly_average_wage_year.st <- year(hourly_average_wag.st$REF_DATE[1])
hourly_average_wage_month.st <- month(hourly_average_wag.st$REF_DATE[1])
#transfer data to the time series time
c(hourly_average_wage_year.st, hourly_average_wage_month.st)
hourly_average_wage.ts <-ts(hourly_average_wag.st$VALUE, start = c(hourly_average_wage_year.st, hourly_average_wage_month.st), freq = 12)
plot(hourly_average_wage.ts)

log_hourly_average_wage.ts <- diff(log(hourly_average_wage.ts))

checkresiduals(log_hourly_average_wage.ts)
adf.test(log_hourly_average_wage.ts *100)

#checkresiduals(diff_hourly_average_wage.ts)
#The data got strong seasonality
#do other seasonal different. 
#Check the staionarlity
##statioanry check
adf.test(diff_hourly_average_wage.ts)
# p-value smaller than printed p-value
kpss.test(seasonaldiff_diff_hourly_average_wage.ts)
######
#The data is stationary.
#we can keep going!
Can_month_housing_sell_GDP_model.ts <- ts(Can_housing_sell_data.raw$Canada, start = c(2007,1), end = c(2022,12), frequency =12)

housing_sell_plus_hourly_wage_model<- auto.arima(Can_month_housing_sell_GDP_model.ts, 
                                                 xreg=(log_hourly_average_wage.ts*100), 
                                                 approximation = FALSE, parallel = T, stepwise = FALSE,
                                                 max.P = 5, max.Q = 5, max.D = 5,
                                                 max.d = 5, max.p = 5, max.q = 5)
#Regression with ARIMA(1,1,3) errors 
summary(housing_sell_plus_hourly_wage_model)


x <- 36
# initialize an empty vector to store the values
values <- numeric(length = x)
for (i in 1:x) {
  values[i] <- 20
  }
The_wage_incerase_rata <- print(values)

housing_sell_plus_hourly_wage_model_forecast <- forecast( housing_sell_plus_hourly_wage_model, h = 36, xreg = The_wage_incerase_rata)
autoplot(housing_sell_plus_hourly_wage_model_forecast)


###### how about the housing sell with the despotiable income? 
# Canadian disposable income, quarterly, seasonally adjusted
CA_disable_income.raw <- "v62305869"
CA_disable_income.st <- get_cansim_vector(CA_disable_income.raw, start_time = "2007-01-01", end_time = "2022-12-01")
CA_disable_income_year.st <- year(CA_disable_income.st$REF_DATE[1])
CA_disable_income_month.st <- month(CA_disable_income.st$REF_DATE[1])
#transfer data to the time series time
c(CA_disable_income_year.st, CA_disable_income_month.st)
CA_disable_income.ts <-ts(CA_disable_income.st$VALUE, start = c(CA_disable_income_year.st, CA_disable_income_month.st), freq = 4)
autoplot(CA_disable_income.ts)

#####stationary data

diff_log_CA_disable_income.ts <- diff(log(CA_disable_income.ts), lag = 1)
adf.test(diff_log_CA_disable_income.ts)
checkresiduals(diff_log_CA_disable_income.ts)

#### now the data is stationary, the next step is turn the housing sell data into quarternally data

#start at 2007q2
Can_month_housing_sell_quarterly.ts <- ts(Can_housing_sell_data.raw$Canada, start = c(2007, 4), end = c(2022, 12), frequency = 12)

# Convert to zoo object for easy aggregation
monthly_data_zoo <- zoo(Can_month_housing_sell_quarterly.ts, order.by = index(Can_month_housing_sell_quarterly.ts))

# Aggregate to quarterly frequency by taking the average of every three consecutive months
Can_month_housing_sell_quarterly_data <- aggregate(monthly_data_zoo, as.yearqtr, mean)

### now its the quarterly data .

housing_sell_plus_disposable_income_model<- auto.arima(Can_month_housing_sell_quarterly_data, 
                                                 xreg=(diff_log_CA_disable_income.ts*100), 
                                                 approximation = FALSE, parallel = T, stepwise = FALSE,
                                                 max.P = 5, max.Q = 5, max.D = 5,
                                                 max.d = 5, max.p = 5, max.q = 5)
print(housing_sell_plus_disposable_income_model)

#Three different situion on


x <- 6
# initialize an empty vector to store the values
values <- numeric(length = x)
for (i in 1:x) {
  values[i] <- -2
}
The_dispoable_income_change_rate <- print(values)

housing_sell_plus_disposable_income_model_forecast <- forecast( housing_sell_plus_hourly_wage_model, h = 6, xreg = The_dispoable_income_change_rate)
autoplot(housing_sell_plus_disposable_income_model_forecast)

########## how is the relationship between the new housing start.

## import the data. 

The_housing_start.raw <- "v52300157"
The_housing_start.st <- get_cansim_vector(The_housing_start.raw, start_time = "2007-01-01", end_time = "2022-12-01")
The_housing_start_year.st <- year(The_housing_start.st$REF_DATE[1])
The_housing_start_month.st <- month(The_housing_start.st$REF_DATE[1])
#transfer data to the time series time
c(The_housing_start_year.st, The_housing_start_month.st)
The_housing_start.ts <-ts(The_housing_start.st$VALUE, start = c(The_housing_start_year.st, The_housing_start_month.st), freq = 12)
autoplot(The_housing_start.ts)

adf.test(diff(log(The_housing_start.ts)))
#one different is enough. 

diff_The_housing_start.ts <- (diff(log(The_housing_start.ts)))
Can_month_housing_sell_evil.ts <- ts(Can_housing_sell_data.raw$Canada, start = c(2007, 2), end = c(2022, 12), frequency = 12)

housing_sell_plus_The_housing_start_model<- auto.arima(Can_month_housing_sell_evil.ts, 
                                                       xreg=(diff_The_housing_start.ts), 
                                                       approximation = FALSE, parallel = T, stepwise = FALSE,
                                                       max.P = 5, max.Q = 5, max.D = 5,
                                                       max.d = 5, max.p = 5, max.q = 5)
print(housing_sell_plus_The_housing_start_model)
#Regression with ARIMA(1,1,3) errors 


x <- 12
# initialize an empty vector to store the values
values <- numeric(length = x)
for (i in 1:x) {
  values[i] <- 0.2
}
new_housing_building_rate <- print(values)

housing_sell_plus_The_housing_start_model_forecast <- forecast(PI = T, housing_sell_plus_The_housing_start_model, h = 12, xreg = new_housing_building_rate)
autoplot(housing_sell_plus_The_housing_start_model_forecast)
```







